Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
write defns for initial ideal, grobner basis

\todo{write below part}
For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial(0)=0$.  Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.  We define the \textbf{initial ideal} $\initial(I)$ to be the ideal generated by $\{\initial(f) : f \in I\}$.  A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subseteq I$ such that 
+\[ \langle \initial(f_1),\dots,\initial(f_n) \rangle = \initial(I). \]

\begin{rem}
A Gr\"obner basis for $I$ \emph{a priori} depends on a choice of basis for the ambient graded polynomial ring.
\end{rem}

>>>>

Now we give brief definitions of initial terms and Gr\"{o}bner
bases. These will be used in the proofs of the inductive lemmas
in Section ~\ref{sec:induction} and in the proof of Theorem
~\ref{thm:main}.

\begin{defn}
\label{defn:initial-term}
Let $f \in k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a homogeneous
polynomial. The \textbf{initial term} $\initial(f)$ of $f$
is the largest monomial in the support of $f$ with respect to
the ordering $\prec$. Furthermore, we set $\initial(0) := 0$.
\end{defn}

Given a homogeneous ideal $I \subseteq k[x_{d_1, 1}$, $\ldots$,
$x_{d_n, n}]$, we can now define the \textbf{initial ideal}
$\initial(I)$ of $I$.

\begin{defn}
\label{defn:initial-ideal}
Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
$x_{d_n, n}]$. Then the initial ideal $\initial(I)$ of $I$ is
the ideal generated by the initial terms of homogeneous polynomials
in $I$:
\[
	\initial(I) := \langle \initial(f) \rangle_{f \in I}
\]
\end{defn}

Furthermore, we will use Gr\"{o}bner bases, which are bases
for these initial ideals and have many useful properties.

\begin{defn}
\label{defn:grobner-basis}
Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
$x_{d_n, n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
\textbf{standard basis} for $I$, is a set of elements in $I$
such that their initial terms form a basis for the initial
ideal of $I$.
\end{defn}
